Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-06-13 manuscript.Rmd
Finish analyse

```{r setup, include = FALSE}
library("papaja")
library(bibliometrix)
library(revtools)
library(bib2df)
```
<!-- Reviewer suggestions:
Kristin Buss -->

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
Papers were screened based on two main criteria:
First, papers had to address emotion regulation, emotional problems, or similar.
Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \@ref(prismachart).
In total, `r nrow(recs_final)` papers were retained for analysis.

@@

## Corpus description

```{r, eval = FALSE}
# Plot papers per year
df_plot <- as.data.frame(table(recs_final$PY), stringsAsFactors = FALSE)
df_plot$Year = as.numeric(df_plot$Var1)
ggplot(df_plot, aes(x= Year, y= Freq))+geom_point() + geom_path(group =1)+
  theme_bw() + scale_y_log10()
```

@@

To map the cooccurrence of terms within documents,
it is pertinent to select the most common terms, instead of using IDF.
As a cutoff, we required terms to occur in at least $0.5%$ of documents.
This selection criterion resulted in a corpus of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
The marginal occurrence of the selected terms is displayed in Figure \@ref(study1wordcloud).
To determine the frequency with which terms were addressed in documents,
we constructed a term-document matrix

```{r study1wordcloud, fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
knitr::include_graphics("study1_wordcloud.png")
```

>>>>

```{r setup, include = FALSE}
library("papaja")
library(bibliometrix)
library(revtools)
library(bib2df)
library(knitr)
library(kableExtra)
run_everything = FALSE
```
<!-- Reviewer suggestions:
Kristin Buss -->

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
Papers were screened based on two main criteria:
First, papers had to address emotion regulation, emotional problems, or similar.
Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \@ref(fig:prismachart).
In total, `r nrow(recs_final)` papers were retained for analysis.

@@

<!--
## Corpus description

{r, eval = FALSE}
# Plot papers per year
df_plot <- as.data.frame(table(recs_final$PY), stringsAsFactors = FALSE)
df_plot$Year = as.numeric(df_plot$Var1)
ggplot(df_plot, aes(x= Year, y= Freq))+geom_point() + geom_path(group =1)+
  theme_bw() + scale_y_log10()
-->

@@

Next, we mapped the cooccurrence of terms within documents as an undirected graph.
When examining cooccurrence,
it is pertinent to select the most common terms, instead of using TF-IDF.
We retained terms present in at least $0.5%$ of the entire corpus,
resulting in a selection of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
The marginal occurrence of the selected terms is displayed in Figure \@ref(fig:study1wordcloud).
This indicates how frequently each term occurred in the corpus, and illustrates what this body of literature is about.

```{r study1wordcloud, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
knitr::include_graphics("study1_wordcloud.svg")
```

Based on our theoretical review, each of the selected terms was coded as being either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' (a closely related construct) of emotion dysregulation.
We stress that this is a simplification; many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017]. Figure \@ref(fig:study1network) displays the term cooccurrence matrix as a force directed graph.
<!--The classification is presented in Table \@ref(tab:study1table1).

r study1table1, results = "asis"}
df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
apa_table(df, escape = F)
-->

```{r study1network, out.width = "100%", fig.cap="Force directed graph for Study 1 co-occurrence analysis. Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation. Two different layouts are presented to aid interpretation."}
#knitr::include_graphics("study1_network1.svg")
library(cowplot)
fig_svg <- cowplot::ggdraw()+cowplot::draw_image("study1_network1.svg")
plot(fig_svg)
```

## Results

```{r}
notingraph <- names(topterms)[!names(topterms) %in% unique(c(edg$term1, edg$term2))]
notingraph <- categ[categ$name %in% notingraph, ]
notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and ", i[length(i)])})
```

Inspecting the co-occurrence graph for the keyword data,
it is evident that there are relatively few interconnections between elements,
with a matrix sparsity 
it becomes evident that emotion dysregulation is the most common and central construct,
as could be expected based on the search terms.
Most of the other constructs in the corpus are directly linked to emotion dysregulation,
which suggests that our search was successful in identifying factors considered to be relevant
for adolescents' emotion dysregulation.
The fact that only few of the constructs were interrelated substantiates our impression that this literature is somewhat fragmented.
One emergent cluster of interrelated constructs pertains to the mental health-related outcomes of emotion dysregulation, most notably anxiety, depression, and externalizing symptoms.

A more surprising finding is that some of the most prevalent terms were not connected to emotion dysregulation -
for example, *Rumination*, only showed a direct link with *Depression*.
Other prevalent terms are entirely absent from Figure \@ref(fig:study1network), as they were not related
to any other terms in the main network. 
These terms, which are displayed in Figure \@ref(fig:study1wordcloud), include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.

## Discussion

Several of these constructs represent active ongoing areas of research - such as the role of fathers in adolescents' emotional development [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@bukowskiPopularityFriendshipEmotional1993], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *Loneliness* [@spithovenItAllTheir2017].
The absence of these terms from the graph thus does not reflect so much a lack of importance.
Rather, these constructs - being important, but not yet well-integrated in the literature,
are prime candidates for future research;
particularly in conjunction with more well-established constructs.
